Probing internal structure of distant quasars using Microlensing

### 2014-03-28 paper1/fitting.tex
Updated plots and makefile
minor
first edits

\section{model fitting}

\begin{figure}
  \includegraphics[width=0.95\hsize]{plots/data.eps}
\caption{data}
\end{figure}

\begin{figure}
  \includegraphics[width=0.5\hsize]{plots/Crescent.eps}
  \includegraphics[width=0.5\hsize]{plots/CrescentReverse.eps}\\
  \includegraphics[width=0.5\hsize]{plots/Disk.eps}
  \includegraphics[width=0.5\hsize]{plots/Gauss.eps}
\caption{Model Fitting}
\end{figure}

>>>>

\section{Model fitting and likelihood analysis}

\begin{figure}
\centering
  \includegraphics[width=0.95\hsize]{plots/data_with_error.eps}
\caption{\label{fig:datafitting} data}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=0.45\hsize]{plots/Rp4all.eps}
  \includegraphics[width=0.45\hsize]{plots/Rhalf4all.eps}\\
  \includegraphics[width=0.45\hsize]{plots/Rhalf_RnRp.eps}
  \includegraphics[width=0.45\hsize]{plots/aRp_bRp.eps}

\caption{\label{fig:mcmc} Model Fitting}
\end{figure}

In this section, we attempt to fit and recover the model parameters from the given dataset generated by different source models - crescent, uniform-disk and Gaussian-disk. So broadly we have 9 cases to discuss. We carried out a likelihood analysis on all three parameter set using Markov-chain Monte-Carlo (MCMC).

\subsection{Mock datasets}
The datasets for each source model is in the form of light curves, the brightness of the source observed at different time scale. Figure \ref{fig:datafitting} shows the three datasets. These datasets are generated using the magnification map shown in figure \ref{fig:magnification} between point B and C (direction from C to B). The data assumed was very  ideal, including 200 different data points at regular interval of time. It is worth noticing that the datasets generated using crescent model and uniform disc model resembles much more than the one generated by Gaussian disc model source. This is also very intuitive as uniform disc is a special case in crescent model where $R_n=0$, The fiducial model assumed to generate these mock datasets are:
\begin{equation}
	[R_p, R_n, a, b] = [50.0, 30.0, 15.0, 10.0]  \ \ \ \rm{for\ Crescent\ model},
	\label{eqn:cp}
\end{equation}
\begin{equation}
	R = 50.0 \ \ \ \rm{for\ Uniform\ disc\ model}
\end{equation}

\begin{equation}
	R = 50.0 \ \ \ \rm{for\ Gaussian\ disk\ model}
\end{equation}
\\
where, $R$ being the size of the uniform disc and Gaussian disc source model.

The aim of this exercise was to explore the degeneracies in  various model parameters and recover the correct fiducial model assumed. Also, it can be inferred if one can simply distinguish between circularly symmetric and asymmetric sources or uniform and Gaussian sources.
The errorbars on each data point, in all three datasets, is about 10 percent its value. Also, because we are fitting these datasets with different caustic crossing (point A to B in figure \ref{fig:magnification}), it adds a natural systematic errors on each data point. We also assume the errors are Gaussian distributed.

\subsection{Fitting with crescent model}
First we explored the parameter space for crescent source model and run its likelihood exploration for three different datasets. Here we have four parameters as given by equation \ref{eqn:cp}. Three red curves in top row of figure \ref{fig:mcmc} represents the resulting likelihood of $R_p$, the overall size of the crescent source for three different datasets. Solid red curve in top row and red contours in bottom row of figure \ref{fig:mcmc} represents the crescent fitting with crescent data (cc.chain in figure \ref{fig:mcmc}). All four parameters can be well recovered in this case and the overall likelihood coincides well with the fiducial values assumed and stated in equation \ref{eqn:cp}. It can also be well noticed that the half light radius is degenerate with $R_n/R_p$ or in other words, $R_p$ and $R_n$ are correlated.

In second case, we tried to fit crescent model to disk data (dc.chain in figure \ref{fig:mcmc}). The dashed red line in top row and blue contours in bottom row represents this case. Here one can recover the overall shape of the source, slightly lower than what is recovered in cc.chain case. Infact, the likelihood is higher than the previous case as the data is generated by one parameter only and fitting with four parameter that can also model the noise. Also, the maximum likelihood is achieved close to $R_n = 0$, as already mentioned, this is intuitive as well. The other paramters, $a$ and $b$ are quite arbitary.

In the third case, Gaussian disc data is fit with crescent model (gc.chain). The dot-dashed red line in top row and green contours in bottom row represents this case. In this case, the extent of $R_p$ is broad and the likelihood is smaller than other cases.

Please notice that in top row of figure \ref{fig:mcmc}, the height of the peaks does not represents in likelihood, it is just ensuring that the area under the curve is unity. The likelihood can be estimated from the number in the legend which is the best $\chi^2$.

\subsection{Fitting with uniform disc model}
In this case, we have only one parameter to fit, the outer radius of the uniform disc with uniform intensity. When fitting with crescent data (solid blue line), the maximum likelihood shifts towards higher values of $R$ as compared to the fiducial value (which was 50). Also the maximum likelihood and is very low and the contraints are also very weak. However, when fitting with Gaussian disc (dot-dashed blue line), the likelihood is still very low, but the parameter is tightly constrained. The third case is ideal when fitting uniform disc data (blue dashed line), where the constraints are ideal and also co-incide well with the fiducial value assumed and also likelihood is comparatively better.

\subsection{Fitting with Gaussian disc model}
In the last case, we fit Gaussian disc model to the three datasets (green curves in top row of figure \ref{fig:mcmc}). In this case, when fitted with Gaussian disc data, the likelihood coincide with the fiducial value assumed, in other cases the likelihood is away but weak and very well constrained.

\section{Conclusion and interpretation}
The main results of this work is given in figure \ref{fig:mcmc} and described in the previous section. Here we try to interpret those results and conclude the take away message.

Lets assume that an ideal telescope observes a quasar for a long time and we get the lightcurve with good precision and one can clearly see the event of caustic crossing in the light curve. Now one wants extract the true shape of the source. To comment more specifically, lets assume three cases when the true shape of the source is: crescent, uniform disc and Gaussian disc:

\begin{enumerate}

\item Crescent shape source: if one tries to fit this curve with crescent model, the maximum likelihood will be good and one can recover the true parameters with good precision. In the other two cases, the maximum likelihood will be very bad. Hence this shape can be recovered very well by trusting the maximum likelihood analysis.
\item Uniform disc shape source: if one tries to fit this curve with Gaussian disk model, the likelihood will be very little to disprove it, however, the other two models are inditinguishable with nearly the same likelihood. At this point it does not matter as one can obtain the true result from both disk and crescent model.
\item Gaussian disc shape source: if one tries to fit this curve with uniform disk model, again likelihood will discard this choice. Again the maximum likelihood analysis will point towards the best fitted true model.

\end{enumerate}

At this point, we conclude that maximum likelihood analysis can be well trusted in order to recover true shape and recovering the corresponding parameters.

### 2014-03-28 paper1/theory.tex
Updated plots and makefile
first edits

We start by introducing in a succint manner the gravitational lensing theory that is relevant for microlensing in general and for the scope of the
present paper in particular. For a detailed presentation of the theory the reader is referred to the books and articles that represent the references
of the current section (book by Schneider and others).\\

The general microlensing equation can be written as:
\begin{equation}
\vec{y} =   
 \begin{pmatrix}
  1-\gamma - k & 0 \\
  0 & 1 + \gamma -k \\
 \end{pmatrix} 
\vec{x} - \sum_{i=1}^{n} m_i \frac{\vec{x} - \vec{x_i}}{\left( \vec{x} - \vec{x_i} \right)^2}.
\end{equation}

The equation is valid for a set of $\it{n}$ point (Schwarzschild) lenses placed at coordinates $\vec{x_i}$. $\vec{y}$ represents the coordinates in the source plane for the respective ray, while 
$\vec{x}$ represents the coordinates in the lens plane. Furthermore, $\gamma$ and $k$ are the shear and surface mass density.\\

For the lens mapping a Jacobian can be defined:
\begin{equation} 
A(\vec{x}) = 
 \begin{pmatrix}
  \frac{\partial{y_1}}{\partial{x_1}} & \frac{\partial{y_1}}{\partial{x_2}} \\
  \frac{\partial{y_2}}{\partial{x_1}} & \frac{\partial{y_2}}{\partial{x_2}} \\
 \end{pmatrix}. 
\end{equation}
The determinant of $A(\vec{x})$ is related to the local magnification factor through the equation:

\begin{equation}
\mu(\vec{x}) = \left| \frac{1}{det(A(\vec{x}))} \right|
\end{equation}

@@

The determinant of the Jacobian $A$ can have both positive and negative values depending in which region it is computed. Such regions are well defined and separated
by critical curves where the determinant vanishes. The lens equation maps the critical curves of the lens plane into caustics in the source plane. An example of the caustic 
shape can be seen in the magnification map of |||Figure 1|||.\\

||||||||||||||||||||
||||||Figure 1||||||
||||||||||||||||||||

Along these critical curves in the lens plane or caustics in the source plane,  the magnification $\mu$ is infinite, a result that simply follows from equation ( 
(3). This statement holds only fo infinitesimally small sources. For extended sources the maximum amplification is finite since only an infinitesimally small area of the source
overlaps with the caustics (Schneider Weiss 1986 paper others).

The matrix $A$ at the coordinates of the caustic can have rank 1 or rank 0. If the rank is 1 then the coordinates belong to $fold$ or $cusp$ singularities. For the purpose 
of this paper we are interested only in the behaviour around $fold$ singularities. A condition necessary to distinguish between a fold and cusp singularity is that the
eigenvector of $A$ corresponding to the null eigenvalue is not a tangent vector of the critical curve (Dominik 2008, Schneider Weiss 1992).

@@

The behaviour of the images of a point source and their corresponding magnifications near such a caustic has been thoroughly studied in the past. The reader who is interested in 
understanding the details related to this subject is referred to papers such as Blandford and Narayan 1986, Schneider and Weiss 1986, Gaudi and Petters 2002. For the present paper we only 
summarize the common result:
\begin {equation}
 \mu_{t}(p) = \mu_0 + C_0 \frac{1}{\sqrt{p}} \Theta(p).
\end {equation}
As the previous equation describes the magnification of a point source near a caustic is equal to the sum of the magnification due to other reasons $\mu_0$, assumed to be locally constant,  and a decrease with
the square root of the distance from the fold. The later term becomes activated only after the source enters the region interior to the caustic curves when the stepfunction $\Theta(p)$ become unity. The proportionality
constant $C_0$  is sensible only to the local behaviour of Fermat's potential and units used for the lens plane coordinates $\vec{y}(p,q)$.

@@

\begin{equation}
 F(t) = \int_{-\infty}^\infty \int_{-\infty}^\infty S_{2D}(p-p_s(t), q-q_s(t)) \mu_t(p) \mathrm{d}q \mathrm{d}p
\end{equation}

@@

\begin{equation}
 F(t) 
= \int_{-\infty}^\infty  \mu_t(p) S_{1D}\left(p-p_s(t)\right) \mathrm{d}p,
\end{equation}

where we have defined the one dimensional flux function as:
\begin{equation}
 S_{1D}(p-p_s(t)) = \int_{-\infty}^\infty S_{2D}(p-p_s(t), q-q_s(t)) \mathrm{d}q
\end{equation}

@@

In the present study we are analysing three types of sources with different surface brighness: 
\begin{enumerate}
 \renewcommand{\theenumi}{(\arabic{enumi})}
  \item a rotationally symmetric source with a bivariate gaussian surface brightness distribution,
  \item a disk source with constant surface brightness distribution,
  \item a crescent shaped source with constant surface brightness distribution.
\end{enumerate}
The first two sources are the typical choices used in the literature to describe the luminous parts of a quasar (Prasenjit should give some citations here). The third one is a newly proposed
variant (Kammrudin 2013 Geometric crescent).

@@

\begin{equation}
 S_{2D}^G(p-p_s, q-q_s) = \frac{S_0^G}{2 \pi \sigma^2} e^{-\frac{(p-p_s)^2}{2 \sigma^2}} e^{-\frac{(q-q_s)^2}{2 \sigma^2}}.
\end{equation}

The corresponding 1D brightness is:

\begin{equation}
 S_{1D}^G(p-p_s) = \frac{S_0^G}{\sqrt{2 \pi} \sigma} e^{-\frac{(p-p_s)^2}{2 \sigma^2}}.
\end{equation}

Other parameters of the model are the total flux $S_0^G$ and $\sigma$.

Although such a definition for a source would have non-zero surface/linear brightness for any coordinate $p,q$, the amount of light received by a detector from outside a $3 \sigma$ disk centered at $p_s, q_s$ 
would be insignificant.

@@

\begin{equation}
 S_{1D}^D(p-p_s) = \frac{2 S_0^D}{\pi R}  \sqrt{1 - \frac{(p-p_s)^2}{R^2} }    \Theta \left( R^2 - \left( p-p_s \right)^2 \right).
\end{equation}

@@

\begin{equation}
 S_{2D}^C =  S_{2D}^{Dp} -  S_{2D}^{Dn}   (n+1)
\end{equation}
with\\

\begin{equation}
 S_{2D}^{Dp}(p-p_{sn}, q-q_{sn}) = \frac{S_0^{Dp}}{\pi R_p^2} \Theta \left( R_p^2 - \left( p-p_{sp} \right)^2 - \left( q-q_{sp} \right)^2 \right)
\end{equation}

and\\
\begin{equation}
 S_{2D}^{Dn}(p-p_{sn}, q-q_{sn}) = \frac{S_0^{Dn}}{\pi R_n^2} \Theta \left( R_n^2 - \left( p-p_{sn} \right)^2 - \left( q-q_{sn} \right)^2 \right).
\end{equation}

The following notations were used: $R_p, (p_{sp}, q_{sp}), R_n, (p_{sn},q_{sn})$ are the radii and coordinate of the center for the larger positive disk and smaller negative disk.  
$S_0^{Dp},S_0^{Dn}$ represent the total flux of radiation received from the large and small disk. From this point forward we will not use the total flux from each source. Instead we will 
use the difference which in this case is th total flux from the crescent-shaped source $S_0^C$. \\
Equation(n+1) can be written as:\\

\begin{align}
 S_{2D}^C &= \frac{S_0^C}{\pi \left(R_p^2-R_n^2 \right)} \left\{ \Theta \left[ R_p^2 - \left( p-p_{sp} \right)^2 - \left( q-q_{sp} \right)^2 \right] \right.\nonumber\\
 &\qquad \left. {} -  \Theta \left[ R_n^2 - \left( p-p_{sn} \right)^2 - \left( q-q_{sn} \right)^2 \right] \right\}.
\end{align}

Analogous for the linear brightness function:

@@

--------------------------------------------------------------------------
Figure with 2d 1d brightness for gaussian, disk, some crescent
----------------------------------------------------------------------------

@@

For the distances between the centers of the two disks we will use the same notations as the one found in the paper [Geometric crescent], $a \equiv p_{sn} - p_{sp}$ and $b \equiv q_{sn} - q_{sp}$.

@@

Using equation (7) and the one-dimensional flux function presented in the previous section one can compute numerically the lightcurves of the three extented sources fot the simplified 
infinite-wall-caustics model.

@@

The amount of light received by an observer from a source with a gaussian distributed brightness with $\sigma$ and total flux $S_0^G$ in the absence of any gravitational lensing is:
\begin{equation}
 F^G(t) = \int_{-\infty}^\infty  \left( \mu_0 + \frac{C_0}{\sqrt{p}} \Theta \left( p \right) \right) \left( \frac{S_0^G}{\sqrt{2 \pi} \sigma} e^{-\frac{(p-p_s(t))^2}{2 \sigma^2}} \right) \mathrm{d}p.
\end{equation}
which can be simplified to:
\begin{equation}
 F^G(t) = \mu_0 S_0^G + \frac{C_0 S_0^G}{\sqrt{2\pi} \sigma} \int_{0}^\infty \frac{e^{-\frac{(p-p_s(t))^2}{2 \sigma^2}}}{\sqrt{p}} \mathrm{d}p.
\end{equation}
The result is equivalent to the one obtained in papers such as (citations).\\

\begin{figure}
\includegraphics[bb = 0 0 600 400]{lightcurve_crescent_1.pdf}
\caption{Lightcurve 1.}
\end{figure}

@@

which is equivalent to:
\begin{equation}
 F^D(t) = \mu_0 S_0^D + \frac{2 C_0 S_0^D}{\pi R} \int_{max(0, p_s(t) - R)}^{max(0, p_s(t) + R)} \frac{1}{\sqrt{p}} \sqrt{1 - \frac{\left( p-p_s(t) \right)^2}{R^2}} \mathrm{d}p.
\end{equation}
As obtained in preciding papers by (citations).\\

\begin{figure}
\includegraphics[bb = 0 0 600 400]{lightcurve_gaussian_1.pdf}
\caption{Lightcurve 2.}
\end{figure}

@@

The lightcurve of a crescent shaped source with unamplified flux $S_0^C$, radii $R_p$, $R_n$ and center displacement $a(t)$ is:
\begin{equation}
 F^c(t) = \mu_0 S_0^C + C_0 \frac{2 S_0^C}{\pi \left( R_p^2 -R_n^2 \right) } 
\left(\int_{max(0, p_s(t) - R)}^{max(0, p_s(t) + R)} \sqrt{\frac{R_p^2 - \left( p-p_s(t) \right)^2 }{p}} \mathrm{d}p 
  -  \int_{max(0, p_s(t) - a(t) - R)}^{max(0, p_s(t) -a(t) + R)} \sqrt{\frac{R_p^2 - \left( p-p_s(t) +a(t) \right)^2 }{p}}  \mathrm{d}p \right)
\end{equation}

In the previous equation we have renamed the coordinate of the center of the large disk $p_{sp}$ to $p_{s}$.  \\

\begin{figure}
\includegraphics[bb = 0 0 600 400]{lightcurve_disc_1.pdf}
\caption{Lightcurve 3.}
\end{figure}

>>>>

We start by introducing in a succint manner the gravitational lensing theory that is relevant for microlensing in general and for the scope of the
present paper in particular. For a detailed presentation of the theory the reader is referred to the books and articles that represent the references
of the current section (book by Schneider and others). The general microlensing equation can be written as:
\begin{equation}
\vec{y} =   
 \begin{pmatrix}
  1-\gamma - k & 0 \\
  0 & 1 + \gamma -k \\
 \end{pmatrix} 
\vec{x} - \sum_{i=1}^{n} m_i \frac{\vec{x} - \vec{x_i}}{\left( \vec{x} - \vec{x_i} \right)^2}.
\label{eqn:microlensingequation}
\end{equation}

The equation is valid for a set of $\it{n}$ point (Schwarzschild) lenses placed at coordinates $\vec{x_i}$. $\vec{y}$ represents the coordinates in the source plane for the respective ray, while $\vec{x}$ represents the coordinates in the lens plane. Furthermore, $\gamma$ and $k$ are the shear and surface mass density. For the lens mapping, a Jacobian can be defined:
\begin{equation} 
A(\vec{x}) = 
 \begin{pmatrix}
  \frac{\partial{y_1}}{\partial{x_1}} & \frac{\partial{y_1}}{\partial{x_2}} \\
  \frac{\partial{y_2}}{\partial{x_1}} & \frac{\partial{y_2}}{\partial{x_2}} \\
 \end{pmatrix}. 
\end{equation}
The determinant of $A(\vec{x})$ is related to the local magnification factor through the equation:

\begin{equation}
\mu(\vec{x}) = \left| \frac{1}{det(A(\vec{x}))} \right|
\label{eqn:mu_x}
\end{equation}

@@

The determinant of the Jacobian $A$ can have both positive and negative values depending in which region it is computed. Such regions are well defined and separated
by critical curves where the determinant vanishes. The lens equation maps the critical curves of the lens plane into caustics in the source plane. An example of the caustic 
shape can be seen in figure \ref{fig:magnification}.\\

\begin{figure}
\centering
  \includegraphics[width=0.95\hsize]{plots/magnification.eps}
\caption{\label{fig:magnification} Magnification map}
\end{figure}

Along these critical curves in the lens plane or caustics in the source plane,  the magnification $\mu$ is infinite, a result that simply follows from equation \ref{eqn:mu_x}. This statement holds only for infinitesimally small sources. For extended sources the maximum amplification is finite since only an infinitesimally small area of the source
overlaps with the caustics \citep{1986BAAS...18T.907S,}.

The matrix $A$ at the coordinates of the caustic can have rank 1 or 0. If the rank is 1 then the coordinates belong to $fold$ or $cusp$ singularities. For the purpose 
of this paper we are interested only in the behaviour around $fold$ singularities. A condition necessary to distinguish between a fold and cusp singularity is that the
eigenvector of $A$ corresponding to the null eigenvalue is not a tangent vector of the critical curve \citep{1992A&A...260....1S,}(Dominik 2008).

@@

The behaviour of the images of a point source and their corresponding magnifications near such a caustic has been thoroughly studied in the past. The reader who is interested in 
understanding the details related to this subject is referred to papers such as \cite{1986ApJ...310..568B}, \cite{1992A&A...260....1S,}, \cite{2002ApJ...574..970G}, \cite{2002ApJ...580..468G}. For the present paper we only 
summarize the common result:
\begin {equation}
 \mu_{t}(p) = \mu_0 + C_0 \frac{1}{\sqrt{p}} \Theta(p).
\end {equation}
As the previous equation describes the magnification of a point source near a caustic is equal to the sum of the magnification due to other reasons $\mu_0$, assumed to be locally constant,  and a decrease with
the square root of the distance from the fold. The later term becomes activated only after the source enters the region interior to the caustic curves when the stepfunction $\Theta(p)$ become unity. The proportionality
constant $C_0$  is sensible only to the local behaviour of Fermat's potential and units used for the lens plane coordinates $\vec{y}(p,q)$.

@@

\begin{equation}
 F(t) = \int_{-\infty}^\infty \int_{-\infty}^\infty S_{2D}(p-p_s(t), q-q_s(t)) \mu_t(p) \mathrm{d}q \mathrm{d}p
 \label{eqn:ft2d}
\end{equation}

@@

\begin{equation}
 F(t) 
= \int_{-\infty}^\infty  \mu_t(p) S_{1D}\left(p-p_s(t)\right) \mathrm{d}p,
\label{eqn:ft}
\end{equation}
\\
where we have defined the one dimensional flux function as:
\begin{equation}
 S_{1D}(p-p_s(t)) = \int_{-\infty}^\infty S_{2D}(p-p_s(t), q-q_s(t)) \mathrm{d}q
\end{equation}

@@

In the present study we are analysing three types of sources with different surface brightness: 
\begin{enumerate}
 \renewcommand{\theenumi}{(\arabic{enumi})}
  \item a rotationally symmetric source with a bivariate gaussian surface brightness distribution,
  \item a disk source with constant surface brightness distribution,
  \item a crescent shaped source with constant surface brightness distribution.
\end{enumerate}
The first two sources are the typical choices used in the literature to describe the luminous parts of a quasar (Prasenjit should give some citations here). The third one is a newly proposed
variant \citep{2013MNRAS.434..765K}.

@@

\begin{equation}
 S_{2D}^G(p-p_s, q-q_s) = \frac{S_0^G}{2 \pi \sigma^2} e^{-\frac{(p-p_s)^2}{2 \sigma^2}} e^{-\frac{(q-q_s)^2}{2 \sigma^2}}.
\end{equation}
\\
The corresponding 1D brightness is:

\begin{equation}
 S_{1D}^G(p-p_s) = \frac{S_0^G}{\sqrt{2 \pi} \sigma} e^{-\frac{(p-p_s)^2}{2 \sigma^2}}.
\end{equation}
\\
Other parameters of the model are the total flux $S_0^G$ and $\sigma$.

Although such a definition for a source would have non-zero surface/linear brightness for any coordinate $p,q$, the amount of light received by a detector from outside a $3 \sigma$ disk centered at $p_s, q_s$ 
would be insignificant. For a gaussian distributed surface brightness source the half-light radius is directly proportional to the parameter $\sigma$ according to the equation:
\begin{equation}
r_{1/2} = \sqrt{ln(4)} \sigma.
\end{equation}

@@

\begin{equation}
 S_{1D}^D(p-p_s) = \frac{2 S_0^D}{\pi R}  \sqrt{1 - \frac{(p-p_s)^2}{R^2} }    \Theta \left( R^2 - \left( p-p_s \right)^2 \right).
\end{equation}
\\
The half-light radius of a uniform disk source is $R/\sqrt{2}$.

@@

\begin{equation}
 S_{2D}^C =  S_{2D}^{Dp} -  S_{2D}^{Dn}   (n+1)
 \label{eqn:s2d}
\end{equation}
with\\

\begin{equation}
 S_{2D}^{Dp}(p-p_{sn}, q-q_{sn}) = \frac{S_0^{Dp}}{\pi R_p^2} \Theta \left( R_p^2 - \left( p-p_{sp} \right)^2 - \left( q-q_{sp} \right)^2 \right)
\end{equation}
\\
and
\begin{equation}
 S_{2D}^{Dn}(p-p_{sn}, q-q_{sn}) = \frac{S_0^{Dn}}{\pi R_n^2} \Theta \left( R_n^2 - \left( p-p_{sn} \right)^2 - \left( q-q_{sn} \right)^2 \right).
\end{equation}
\\
The following notations were used: $R_p, (p_{sp}, q_{sp}), R_n, (p_{sn},q_{sn})$ are the radii and coordinate of the center for the larger positive disk and smaller negative disk respectively.  $S_0^{Dp},S_0^{Dn}$ represent the total flux of radiation received from the large and small disk. From this point forward we will not use the total flux from each source. Instead we will 
use the difference which in this case is th total flux from the crescent-shaped source $S_0^C$. \\
Equation \ref{eqn:s2d} can be written as:\\

\begin{align}
 S_{2D}^C &= \frac{S_0^C}{\pi \left(R_p^2-R_n^2 \right)} \left\{ \Theta \left[ R_p^2 - \left( p-p_{sp} \right)^2 - \left( q-q_{sp} \right)^2 \right] \right.\nonumber\\
 &\qquad \left. {} -  \Theta \left[ R_n^2 - \left( p-p_{sn} \right)^2 - \left( q-q_{sn} \right)^2 \right] \right\}.
\end{align}
\\
Analogous for the linear brightness function:

@@

@@

For the distances between the centers of the two disks we will use the same notations as the one found in the paper \citep{2013MNRAS.434..765K}, $a \equiv p_{sn} - p_{sp}$ and $b \equiv q_{sn} - q_{sp}$.

@@

Using equation \ref{eqn:ft} and the one-dimensional flux function presented in the previous section one can compute numerically the lightcurves of the three extented sources for the simplified 
infinite-wall-caustics model.

@@

The amount of light received by an observer from a source with a gaussian distributed brightness with $\sigma$ and total flux $S_0^G$ in the absence of any gravitational lensing is:
\begin{equation}
 F^G(t) = \int_{-\infty}^\infty  \left( \mu_0 + \frac{C_0}{\sqrt{p}} \Theta \left( p \right) \right) \left( \frac{S_0^G}{\sqrt{2 \pi} \sigma} e^{-\frac{(p-p_s(t))^2}{2 \sigma^2}} \right) \mathrm{d}p.
\end{equation}
which can be simplified to:
\begin{equation}
 F^G(t) = \mu_0 S_0^G + \frac{C_0 S_0^G}{\sqrt{2\pi} \sigma} \int_{0}^\infty \frac{e^{-\frac{(p-p_s(t))^2}{2 \sigma^2}}}{\sqrt{p}} \mathrm{d}p.
\end{equation}
Figure \ref{fig:lightcurve_gauss} shows the corresponding lightcurve. The result is equivalent to the one obtained in papers such as (citations).\\

\begin{figure}
\includegraphics[width = .8\textwidth]{plots/lightcurve_gaussian_1.eps}
\caption{\label{fig:lightcurve_gauss} Lightcurve 1.}
\end{figure}

@@

which is equivalent to:
\begin{equation}
 F^D(t) = \mu_0 S_0^D + \frac{2 C_0 S_0^D}{\pi R} \int_{max(0, p_s(t) - R)}^{max(0, p_s(t) + R)} \frac{1}{\sqrt{p}} \sqrt{1 - \frac{\left( p-p_s(t) \right)^2}{R^2}} \mathrm{d}p.
\end{equation}
Figure \ref{fig:lightcurve_disk} shows the corresponding lightcurve. As obtained in preciding papers by (citations).\\

\begin{figure}
\includegraphics[width = .8\textwidth]{plots/lightcurve_disc_1.eps}
\caption{\label{fig:lightcurve_disk} Lightcurve 2.}
\end{figure}

@@

The lightcurve of a crescent shaped source with unamplified flux $S_0^C$, radii $R_p$, $R_n$ and center displacement $a(t)$ is:
\begin{equation}
 F^c(t) = \mu_0 S_0^C + C_0 \frac{2 S_0^C}{\pi \left( R_p^2 -R_n^2 \right) } 
\left(\int_{max(0, p_s(t) - R)}^{max(0, p_s(t) + R)} \sqrt{\frac{R_p^2 - \left( p-p_s(t) \right)^2 }{p}} \mathrm{d}p 
  -  \int_{max(0, p_s(t) - a(t) - R)}^{max(0, p_s(t) -a(t) + R)} \sqrt{\frac{R_p^2 - \left( p-p_s(t) +a(t) \right)^2 }{p}}  \mathrm{d}p \right)
\end{equation}
Figure \ref{fig:lightcurve_crescent} shows the corresponding lightcurve.
In the previous equation we have renamed the coordinate of the center of the large disk $p_{sp}$ to $p_{s}$.  \\

\begin{figure}
\includegraphics[width = .8\textwidth]{plots/lightcurve_crescent_1.eps}
\caption{\label{fig:lightcurve_crescent} Lightcurve 3.}
\end{figure}
